Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
Adding SSI workshops and more background on WSSSPE

\asnote{Should also discuss the WSSSPE~\cite{wssspe} series of workshops in this section}
\scnote{Section 5.8 and Appendix J in \cite{WSSSPE3} has some preliminary work and discussion on the topic.}

>>>>

Most noteable of the community efforts are those of WSSSPE~\cite{wssspe} and SSI~\cite{ssi-workshops} who between them have run a series of workshops aimed at gathering together community memberrs with an interest in improving the status of software in academia. \asnote{Not sure this is a sufficient one-line summary but couldn't think of anything better.} In each of the three years that WSSSPE workshops have run thus far, the participants have produced a report documenting the topics covered. Section 5.8 and Appendix J in \cite{WSSSPE3} has some preliminary work and discussion particularly relevant to this working group.
